### 2023-03-27 paper-thesis/chapters/31-comparing-with-lambdapi.tex
Improve more text

We now define the \emph{reduction rules}, which define how to reduce the language. A rule $a \hookrightarrow b$ states that \verb|a| reduces to \verb|b|. We reduce the constructs in our language to constructors in lambdapi, this is called \emph{embedding} the language. Lambdapi can then evaluate the rules using its own semantics, not requiring any additional rules similar to the ones in figure \ref{fig:beta-head-reduce-rules}. The reduction rules are given in figure \ref{fig:lp-rules}. Each of the constructs is reduced to the corresponding construct in the meta language.

@@

One program which would not type-check with this approach is the following. It fails to compile since it cannot know that \verb|b| is a boolean, which is required by the definition of f. \footnote{Assuming we introduce booleans into the language, there are examples that don't require booleans but they are a bit more difficult to understand}.
\begin{lstlisting}
let T = Bool;
\f: Bool -> Bool;
\b: T. f b
\end{lstlisting}

>>>>

We now define the \emph{reduction rules}, which define how to reduce the language. A rule $a \hookrightarrow b$ states that \verb|a| reduces to \verb|b|. We reduce the constructs in our language to constructors in lambdapi, this is called \emph{embedding} the language. Lambdapi can then evaluate the rules using its own semantics, not requiring any additional rules similar to the ones in figure \ref{fig:beta-head-reduce-rules}. It is also possible to define the rules in \ref{fig:beta-head-reduce-rules} using reduction rules, but this way of defining reduction rules is much simpler. The reduction rules are given in figure \ref{fig:lp-rules}. Each of the constructs is reduced to the corresponding construct in the meta language.

@@

One program which would not type-check with this approach is the following. It fails to compile since it cannot know that \verb|b| is a boolean, which is required by the definition of f \footnote{Assuming we introduce booleans into the language, there are examples that don't require booleans but they are a bit more difficult to understand}.
\begin{lstlisting}
let T = Bool;
\f: Bool -> Bool;
\b: T. f b
\end{lstlisting}

We could solve this problem by not defining our program as an embedding, instead defining it using the reduction rules in figure \ref{fig:beta-head-reduce-rules}. This results in a definition very close to the one in Statix, except that instead of a beta reduction relation we use the reductions built-in to the language, which solves the problem.

We've now discussed equational unification using lambdapi, which is a feature that we suggest could improve Statix. Other possible improvements are discussed in chapter \ref{ch:ergonomics}.

### 2023-03-27 paper-thesis/chapters/40-discussing-statix.tex
Improve more text

\begin{enumerate}
	\item Nested constraints: Defining a constraint that can use the metavariables of a parent constraint. This works similar to nested function definitions. For example, for type checking datatypes:
	\begin{lstlisting}
typeOfExpr_(s, DataTypeDecl(n, ps, is, ue, cs, b)) = ... :-

@@

	\item In order to implement more powerful inference algorithms, it would be useful to have a mechanism to check if metavariables have been instantiated or not. Since the order in which Statix evaluates constraints is so dynamic, we're not entirely sure how this mechanism would be implemented. More research is needed on this.

>>>>

\begin{enumerate}
	\item Allow specifying reduction rules, and then implement equality under reduction in Statix. This feature was discussed extensively in chapter \ref{ch:comp-lambdapi}.

	\item Nested constraints: Defining a constraint that can use the metavariables of a parent constraint. This works similar to nested function definitions. For example, for type checking datatypes:
	\begin{lstlisting}
typeOfExpr_(s, DataTypeDecl(n, ps, is, ue, cs, b)) = ... :-

@@
